%% start of file 'template.tex'.
%% Based on a c.v. template (moderncv) that is Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%% Also based on code by Saad Quadri in latexresu.me
%% modern cv under LaTeX Project Public License version 1.3c
%% latexresu.me under MIT license.
%% Paul Gowder additions under MIT license.

\documentclass[letterpaper]{moderncv}
\usepackage{textcomp}
\usepackage{multicol}
% moderncv themes
\moderncvstyle{classic}           % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{2cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if
%you want to force the width allocated to your name and avoid line breaks. be
%careful though, the length is normally calculated to avoid any overlap with
%your personal info; use this at your own typographical risks...


\usepackage{fontspec}
\renewcommand*{\addressfont}{\small\mdseries}
\renewcommand*{\namefont}{\fontsize{34}{36}\mdseries\upshape\sffamily}
\renewcommand*{\titlefont}{\LARGE\mdseries\upshape\sffamily}
\renewcommand*{\sectionfont}{\Large\bfseries\upshape\sffamily}
\renewcommand*{\subsectionfont}{\large\bfseries\upshape\sffamily}
\setsansfont{CooperHewitt-Medium.ttf}



\usepackage{xpatch}
\xpatchcmd{\cventry}{\slshape#4}{#4}{}{}

\newcommand*{\mycvlistdoubleitem}[3][.25em]{%
  \cvitem[#1]{}{\begin{minipage}[t]{\listdoubleitemcolumnwidth}#2\end{minipage}%
  \hfill% fill of \separatorcolumnwidth
  \ifthenelse{\equal{#3}{}}%
    {}%
    {\begin{minipage}[t]{\listdoubleitemcolumnwidth}#3\end{minipage}}}}



    % Profile
\name{Paul Gowder}{}
\address{Last update: March 15, 2021} %% total hack to get last rev date instead of
                                %% address in here.
\email{paul.gowder@gmail.com}
\homepage{gowder.io}

\begin{document}

\makecvtitle

\lfoot{\thepage}

%
% positions
%
\section{Employment}
\cventry
{2020-}
{Professor of Law}
{Northwestern University}
{Chicago, IL}
{}
{\begin{itemize}%
  \item Research and teaching (across academic positions) in areas of law including constitutional law, torts, race and the law, law and technology, professional ethics.
  \item Publications and other academic accomplishments listed in full c.v. on https://gowder.io, including 2016 book, The Rule of Law in the Real World (Cambridge University Press).
  \end{itemize}}

\cventry
{2012-2020}
{Professor of Law}
{University of Iowa}
{Iowa City, IA}
{}
{Associate Professor of Law (pre-tenure) 2012-17; Professor of Law (tenured); 2017-2020; Professor of Law and O.K. Patton Fellow in Law 2019-20; courtesy appointments in Political Science 2012-20, Philosophy 2016-20.}
%

\cventry
{Fall 2019}
{Visiting Professor of Law}
{Boston University}
{}
{}
{}

\cventry
{2004-6}
{Victor M. Glasberg and Associates}
{Associate Attorney}
{Alexandria, VA}
{}
{\begin{itemize}%
	\item Civil rights litigation in small private public interest firm with caseload including employment discrimination,
    police misconduct, First Amendment, due process and similar subject areas.
	\end{itemize}}

\cventry
{2001-3}
{Oregon Law Center}
{Staff Attorney}
{Ontario, OR}
{}
{\begin{itemize}%
	\item Low-income legal services representation with caseload primarily centered on employment
    (especially farmworker), housing, and public benefits litigation.
	\end{itemize}}

\cventry
{1999}
{ACLU of the National Capital Area}
{Summer Law Clerk}
{Washington, D.C.}
{}
{}


\section{Consulting}

\cventry
{2018-2019}
{Facebook, Inc.}
{Contract Researcher/Consultant}
{Menlo Park, CA}
{}
{\begin{itemize}%
	\item Consulting relating to questions surrounding elections and democratic
    integrity as well as content moderation oversight board.
    Full-time for two months in summer 2018, and then continuing on
    part-time basis thereafter. Formal relationship
    as contractor via Pro Unlimited, Inc.
	\end{itemize}}

\cventry
{07/2016}
{JSTOR Labs}
{Subject matter expert}
{Ann Arbor, CA}
{}
{\begin{itemize}%
	\item Participate as outside expert on a voluntary basis in weeklong design
    sprint relating to potential expansion of scholarly archiving and discovery products.
	\end{itemize}}

%
% education
%
\section{Education}
\cventry
{2012}
{Ph.D., Political Science}
{Stanford University}
{}
{}
{}
\cventry
{2000}
{J.D.}
{Harvard Law School}
{}
{}
{}
\cventry
{1997}
{B.A., Political Science}
{California State University, Los Angeles}
{}
{}
{}


\section{Grants, Awards, Honors}
\cvitem
{2020-}
{American Law Institute, elected member (beginning December 2020).}
\vspace{1mm}
\cvitem
{2020-1}
{Knight Foundation, grant funding (\$100,000) to support research that applies principles from constitutional law and institutional political science to the challenges of platform governance.}
\vspace{1mm}
\cvitem
{2014-5}
{Institute for Advanced Study, Princeton, NJ: Member (School of Social Science).}
\vspace{1mm}
\cvitem
{2014}
{Montreal Political Theory Manuscript Award, Groupe de recherche interuniversitaire en philosophie politique de Montreal (for The Rule of Law in the Real World).}
\vspace{1mm}

\section{Significant Community and Institutional Service}
\cvitem
{2020-1}
{Member, Dean Search Committee, Northwestern University, Pritzker School of Law.}
\vspace{1mm}
\cvitem
{2020-1}
{Member, Faculty Advisory Council, Northwestern University, Buffett Institute for Global Affairs.}
\vspace{1mm}
\cvitem
{2019-20}
{Member, Faculty Appointments Committee, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2017-20}
{Advisory Board Member, University of Iowa, Obermann Center for Advanced Studies.}
\vspace{1mm}
\cvitem
{2016-7}
{Member, Diversity Committee, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2016-20}
{Faculty Adviser, Black Law Students Association, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2016-}
{Faculty Advisor, American Constitution Society Student Chapter, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2015-9}
{Service on one S.J.D. committee, and (2016-) adviser to another, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2015-6}
{Chair, Speakers Committee, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2014, 6}
{Faculty Advisor, AAI Moot Court Problem Creation, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2012-8}
{Judge, AAI Moot Court, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2012-4}
{Member, Speakers Committee, University of Iowa, College of Law.}
\vspace{1mm}
\cvitem
{2010-11}
{Graduate Admissions Committee, Stanford University, Department of Political Science.}
\vspace{1mm}
\cvitem
{2008}
{Graduate Organizer, Political Theory Workshop, Stanford University, Department of Political Science.}
\vspace{1mm}
\cvitem
{2008}
{Graduate Organizer (interim), Global Justice Workshop, Stanford University, Department of Political Science.}
\vspace{1mm}
\cvitem
{2008}
{Chair, Ad Hoc Graduate Incentives Committee, Political Science Graduate Students Association, Stanford University, Department of Political Science.}
\vspace{1mm}
\cvitem
{2007-8}
{Social Chair, Political Science Graduate Students Association, Stanford University, Department of Political Science.}
\vspace{1mm}
\cvitem
{1999-2000}
{Public Relations Chair, Harvard Law School, Student Public Interest Network.}
\vspace{1mm}


\vspace{1mm}
\subsection{Community Service and Outreach}
\cvitem
{2016-9}
{Member, Iowa City Telecommunications Commission.}
\vspace{1mm}
\cvitem
{2016}
{Panelist: 'Family Law', Iowa LGBT Rural Summit (USDA/National Center for Lesbian Rights/Drake Law School).}
\vspace{1mm}
\cvitem
{2016}
{Presentation, 'Loving v. Virginia,' African-American Museum of Iowa/Cedar Rapids Public Library.}
\vspace{1mm}
\cvitem
{2015, 6}
{Guest blogger, Prawfsblawg.}
\vspace{1mm}
\cvitem
{2015}
{Presentation, 'The Leadership Rationale,' The Past, Present, \& Future of Diversity and Inclusion Within the Central Iowa Legal Community.}
\vspace{1mm}
\cvitem
{2014}
{Editorial, "Court Moves Toward Death for Contraceptive Coverage": Des Moines Register,.}
\vspace{1mm}
\cvitem
{2014}
{Panelist, Ethical Perspectives on the News: KCRG TV (discussing religion and public life, Hobby Lobby, etc.).}
\vspace{1mm}
\cvitem
{2014}
{Presentation, Voting Rights in the United States: Iowa Interfaith Alliance, Intersections speaker series.}
\vspace{1mm}
\cvitem
{2013}
{Guest blogger, Concurring Opinions.}
\vspace{1mm}
\cvitem
{2012}
{Editorial: "Independent Judiciary": Cedar Rapids Gazette (with Nicholas Johnson).}
\vspace{1mm}
\cvitem
{2010}
{Presentation: The Law and Ethics of Farm Worker Internships, Cultivating Food Justice Conference.}
\vspace{1mm}
\cvitem
{2005}
{Editorial: "A Naked Assault on the Public and Courts": Oregon State Bar Journal.}
\vspace{1mm}
\cvitem
{2001-3}
{Executive Board Member, Oregon Rural Action.}
\vspace{1mm}
%
% languages
%
\section{Miscellany}

\subsection{Languages}
\cvitem{Human}{English (native). Attic Greek (rudimentary reading, extremely rusty).}
\cvitem{Computer}{ Python (intermediate/advanced).  R (intermediate, rusty).  Clojure (intermediate).  Swift (beginner/intermediate).  Javascript (beginner). }
\subsection{Bar Admissions}
\cvitem{}{ Louisiana, Massachusetts, Oregon, Virginia (bar admissions not currently in active or authorized to practice status; not currently engaged in practice of law)}
\subsection{Less Formal Education}
\cvitem{2017}{Recurse Center (summer 2 half-batch).}
\cvitem{2013}{University College Cork, Attic Greek Summer Immersion.}

\end{document}
